Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-26 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}

@@

\begin{proof}Since $\events'$ is induced by $\mathbf{O}$, it is
commuting. By theorem~\ref{thm:sub-event-space}, there is set~$\Omega$,
a function~$\tau:\events'\rightarrow2^{\Omega}$, and a convex classical
interval-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}=\bar{\mu}'\circ\tau$. Let $\mul[\prime]:\events'\rightarrow\left[0,1\right]$
and $\mur[\prime]:\events'\rightarrow\left[0,1\right]$ are the left-end
and the right-end of $\bar{\mu}'$, respectively, i.e., $\bar{\mu}'\left(E\right)=\left[\mul[\prime]\left(E\right),\mur[\prime]\left(E\right)\right]$
for all $E\in2^{\Omega}$. Consider the random variable~$X:\Omega\rightarrow\mathscr{I}$
defined by $X=\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mathbf{1}_{\tau\left(P_{i}^{-}\right)}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mathbf{1}_{\tau\left(P_{i}^{+}\right)}$.
Then, 
\begin{eqnarray*}
\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\\
 & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right)\right]\\
 & = & \int X\rmd\bar{\mu}'\\
 & = & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu\right]
\end{eqnarray*}
\end{proof}

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}
\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}

@@

\begin{proof}Since $\events'$ is induced by $\mathbf{O}$, it is
commuting. By theorem~\ref{thm:sub-event-space}, there is set~$\Omega$,
a function~$\tau:\events'\rightarrow2^{\Omega}$, and a convex classical
interval-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}=\bar{\mu}'\circ\tau$. Let $\mul[\prime]:\events'\rightarrow\left[0,1\right]$
and $\mur[\prime]:\events'\rightarrow\left[0,1\right]$ are the left-end
and the right-end of $\bar{\mu}'$, respectively, i.e., $\bar{\mu}'\left(E\right)=\left[\mul[\prime]\left(E\right),\mur[\prime]\left(E\right)\right]$
for all $E\in2^{\Omega}$. Consider the random variable~$X:\Omega\rightarrow\mathscr{I}$
defined by $X=\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mathbf{1}_{\tau\left(P_{i}^{-}\right)}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mathbf{1}_{\tau\left(P_{i}^{+}\right)}$.
Then, 
\begin{eqnarray*}
 &  & \expval{\mathbf{O}}_{\bar{\mu}}\\
 & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\\
 & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right)\right]\\
 & = & \int X\rmd\bar{\mu}'\\
 & = & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu',\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu'\right]\\
 & = & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu'\left(\tau\left(P_{i}^{-}\right)\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu'\left(\tau\left(P_{i}^{+}\right)\right),\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu'\left(\tau\left(P_{i}^{-}\right)\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu'\left(\tau\left(P_{i}^{+}\right)\right)\right]\\
 & = & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu\left(P_{i}^{+}\right),\max_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu\left(P_{i}^{+}\right)\right]\\
 & = & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{+}\right),\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{+}\right)\right]\\
 & = & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ ,}
\end{eqnarray*}
where 
\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu'\left(\tau\left(P_{i}^{-}\right)\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu'\left(\tau\left(P_{i}^{+}\right)\right)\le\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu\left(P_{i}^{+}\right)
because $\tau$ in theorem~\ref{thm:sub-event-space} applies to
both real-valued and interval-valued probability measure, for any
$\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)$, there exists
a $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$ such that $\mu=\mu'\circ\tau$.
On the other hand, 
\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu'\left(\tau\left(P_{i}^{-}\right)\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu'\left(\tau\left(P_{i}^{+}\right)\right)\ge\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu\left(P_{i}^{+}\right)
because for any $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$, we
have 
\begin{eqnarray*}
 &  & \mu'\left(E\right)\in\bar{\mu}'\left(E\right)\textrm{ for all }E\in2^{\Omega}\\
 & \Rightarrow & \mu'\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)=\bar{\mu}\left(P\right)\textrm{ for all }P\in\events'
\end{eqnarray*}
Let $\rho=\sum_{i=1}^{N^{-}}\frac{\mu'\left(\tau\left(P_{i}^{-}\right)\right)}{\Tr\left(P_{i}^{-}\right)}P_{i}^{-}+\sum_{i=1}^{N^{+}}\frac{\mu'\left(\tau\left(P_{i}^{+}\right)\right)}{\Tr\left(P_{i}^{+}\right)}P_{i}^{+}$.
Then, we have 
\begin{eqnarray*}
\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{-}\right) & = & \sum_{i=1}^{N^{-}}\frac{\mu'\left(\tau\left(P_{i}^{-}\right)\right)}{\Tr\left(P_{i}^{-}\right)}\Tr\left(P_{i}^{-}P_{j}^{-}\right)+\sum_{i=1}^{N^{+}}\frac{\mu'\left(\tau\left(P_{i}^{+}\right)\right)}{\Tr\left(P_{i}^{+}\right)}\Tr\left(P_{i}^{+}P_{j}^{-}\right)=\mu'\left(\tau\left(P_{j}^{-}\right)\right)\\
\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{+}\right) & = & \sum_{i=1}^{N^{-}}\frac{\mu'\left(\tau\left(P_{i}^{-}\right)\right)}{\Tr\left(P_{i}^{-}\right)}\Tr\left(P_{i}^{-}P_{j}^{+}\right)+\sum_{i=1}^{N^{+}}\frac{\mu'\left(\tau\left(P_{i}^{+}\right)\right)}{\Tr\left(P_{i}^{+}\right)}\Tr\left(P_{i}^{+}P_{j}^{+}\right)=\mu'\left(\tau\left(P_{j}^{+}\right)\right)
\end{eqnarray*}
Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$.\end{proof}
